---
format: pdf
editor: source
execute:
  echo: false
  warning: false
  error: false

---

```{r}
#| include: false

# install the packagesNeeded below if they are absent from your system

packagesNeeded <- c("readr", "dplyr", "flextable")

invisible(lapply(packagesNeeded, library, character.only = TRUE))

```

```{r}

# raw file shows area to the left of specific z-scores
ztable_leftward <- round(read_csv("ztable.csv", col_types = cols()),4)
# remove lines that are all zeros
ztable_leftward_filtered <- ztable_leftward |> 
  filter(if_all(starts_with("0"), ~ . > 0)) |>
  filter(if_all(starts_with("0"), ~ . < 1)) 
ztable_rightward_filtered <- ztable_leftward_filtered |> mutate(across(`0`:`0.09`, ~ 1-.x))

ztable_leftward_filtered <- ztable_leftward_filtered |> mutate(across(`0`:`0.09`, ~ round(.x,4)))
ztable_rightward_filtered <- ztable_rightward_filtered |> mutate(across(`0`:`0.09`, ~ round(.x,4)))

```

# *z*-table (rightward)
**Directions**: To find any particular *z*-score, combine the value in the row in the left-most column (`Z`) with the appropriate value across the top of the rightward columns. For example, the area `to the right` of a *z*-score of `-1.25` would be found by finding the intersection of `-1.2` in the first column with the column labeled `0.05` across the top (This value is 0.8944).

<br/>

```{r}
set_flextable_defaults(fonts_ignore=TRUE)

qflextable(ztable_rightward_filtered) |>
  fit_to_width(max_width=7, inc = 1L, max_iter = 20, unit = "in") |>
  theme_zebra()

```

<br/>

# *z*-table (leftward)
**Directions**: To find any particular *z*-score, combine the value in the row in the left-most column (`Z`) with the appropriate value across the top of the rightward columns. For example, the area `to the left` of a *z*-score of `-1.25` would be found by finding the intersection of `-1.2` in the first column with the column labeled `0.05` across the top (this value is 0.1056).

<br/>

```{r}

set_flextable_defaults(fonts_ignore=TRUE)

qflextable(ztable_leftward_filtered) |>
  fit_to_width(max_width=7, inc = 1L, max_iter = 20, unit = "in") |>
  theme_zebra()

```

